Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box

### 2015-05-08 paper/paper 2/paper 2.tex
feedback Erman

We describe the intended behavior for each constraint type in terms of validation results depending on \emph{CWA} and \emph{UNA}.
If any two constraints are semantically the same (w.r.t. RDF semantics), they should detect the same set of violations regardless of concrete RDF data, 
which means whenever the constraints are applied to any RDF data they point out the same violations or they have the same effect.
To be able to define mappings between semantically equivalent \emph{specific constraints} (expressed by different languages) and 
between \emph{specific constraints} and \emph{generic constraints},
we show for each constraint type that their constraints lead to exactly the same violations which shows that they behave in the same way. 
We expressed constraint types by different languages
to document identical semantics for these languages with regard to appropriate constraint types.

>>>>

We recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as appendix of this paper) in which
we describe the intended behavior of each constraint type in terms of validation results depending on \emph{CWA} and \emph{UNA}.
If any two constraints are semantically the same (w.r.t. RDF semantics), they should detect the same set of violations regardless of RDF data, 
which means whenever the constraints are applied to any RDF data they point out the same violations.
To be able to define mappings between semantically equivalent \emph{specific constraints} (expressed by different languages) and 
between \emph{specific constraints} and \emph{generic constraints},
we show for each constraint type that their constraints lead to exactly the same violations which shows that they behave in the same way. 
We expressed constraint types by different languages
to document identical semantics for these languages with regard to appropriate constraint types.
